Component response rate variation drives stability in large complex systems

### 2018-07-27 notebook/ms_for_review.Rmd
Small changes to text

>>>>

The while loop in `rand_mat_ga` continues until either `iter` generations have occured, a solution $\gamma$ vector is found that results in all $\Re(\lambda) < 0$, or some criteria of minimum fitness increase is observed (by default, `converg = 0.01`). Within the genetic algorithm, $\gamma$ values are mutated, crossover occurs between $\gamma$ vectors, and selection occurs in each generation such that the 20 $\gamma$ vectors that produce the lowest maximum $\Re(\lambda)$ are allowed to have 50 offspring each. In mutation, any $\gamma_{i}$ values that mutate below zero are multiplied by $-1$, and any values that mutate above 2 are set to 2. Note also that if a solution is found, then one such $\gamma$ vector causing stability is printed to a file.
